\begin{CJK}{UTF8}{ipxm}
During the months of writing the thesis, I have encountered many difficulties and obstacles, but now I feel a sense of accomplishment and warmth in my heart when I see the final draft.

First of all, I am deeply indebted to \href{https://paulhorton.gitlab.io/}{Dr. Paul Horton}. Without his guidance, support and kindness, I would never have been able to pursue the Chinese-Japanese translation system as a thesis topic. He has given a lot of foresighted but insightful advice on topic content, essay writing, etc. Every time I communicate with him, I always gain a lot. 長い間、ご指導頂きまして、本當に感謝しております。

Secondly, I would like to thank \href{https://ikmlab.csie.ncku.edu.tw/advisor.html}{Dr. Hung-Yu Kao} and \href{http://mmcv.csie.ncku.edu.tw/~wtchu/}{Dr. Wei-Ta Chu} for agreeing to be my thesis committee despite their extremely busy schedule. I am grateful to them for taking the time to read my thesis and giving it all kinds of useful advice. They are all professors who are passionate about teaching and research, and I believe their academic achievements will continue to increase.

Thirdly, I would like to thank the owners of the information, literature, and ideas cited and referenced in this thesis. Without these constructive and prospective materials, I would not have been able to accomplish my thesis. Thank you to these researchers who are willing to share their knowledge with the world.

Lastly, I would like to thank my family and all my friends. Because of your encouragement, advice, and help, I was able to complete this thesis successfully. 

\end{CJK}

\begin{flushright}
\mbox{Shih-Chieh Wang}
\end{flushright}